Issues Developing the new Abalone MSE

### 2020-05-17 data-raw/development.Rmd
Big changes involving the larval dispersal dynamics, which are now integrated into the dynamics more intuitively. Other functions and examples all changed to match. No Errors, or Warnings, but a note about example files it creates being found?

>>>>

## The Dynamics Described

### The Initial Equilibrium

The unfished equilibrium is a classical starting point for any model, even if a decision is made to begin any simulations at some lower depletion level. We are using a one-year time-step but the dynamics occurs within each year. The dynamic part of the region has the following structure:

regionD - the dynamic part of hte regional structure

* SMU     : num [1:6] 1 1 2 2 2 2
* matureB : num [1:40, 1:6] 782 0 0 0 0 ...
* exploitB: num [1:40, 1:6] 892 0 0 0 0 ...
* catch   : num [1:40, 1:6] 0 0 0 0 0 0 0 0 0 0 ...
* harvestR: num [1:40, 1:6] 0 0 0 0 0 0 0 0 0 0 ...
* cpue    : num [1:40, 1:6] 399 0 0 0 0 ...
* recruit : num [1:40, 1:6] 630563 0 0 0 0 ...
* deplsB  : num [1:40, 1:6] 1 0 0 0 0 0 0 0 0 0 ...
* depleB  : num [1:40, 1:6] 1 0 0 0 0 0 0 0 0 0 ...
* catchN  : num [1:105, 1:40, 1:6] 0 0 0 0 0 0 0 0 0 0 ...
* Nt      : num [1:105, 1:40, 1:6] 6.31e+05 2.34e-06 4.31e-05 ...

This represents the dynamics before any simulations have occurred, the unfished equilibrium state. Similarly, the constant part of the region, made up of a list for each population, has the following structure:

* Me      : num 0.198
* R0      : num 636147
* B0      : num 782
* effB0   : num 782
* ExB0    : num 892
* effExB0 : num 892
* MSY     : num 54.3
* MSYDepl : num 0.304
* bLML    : num 153
* popq    : num 0.000447
* SaM     : num 139
* popdef  : Named num [1:19] 34.45 122.75 164.92 4.61 -16 ....
* LML     : num [1:40] 132 132 132 132 132 132 132 132 132 132 ...
* G       : 'STM' num [1:105, 1:105] 2.12e-13 4.52e-12 8.33e-11 1.27e-09 1.62e-08 ...
* Maturity: num [1:105] 1.42e-07 1.78e-07 2.24e-07 2.83e-07 3.56e-07 ...
* WtL     : num [1:105] 0.000351 0.003438 0.013072 0.033719 0.070319 ...
* Emergent: num [1:105] 1.92e-16 3.44e-16 6.18e-16 1.11e-15 1.99e-15 ...
* Select  : num [1:105, 1:40] 2.87e-127 2.61e-125 2.37e-123 2.16e-121 1.96e-119 ...
* SelWt   : num [1:105, 1:40] 1.01e-130 8.97e-128 3.10e-125 7.28e-123 1.38e-120 ...
* MatWt   : num [1:105] 4.97e-11 6.13e-10 2.93e-09 9.53e-09 2.50e-08 ...
* SMU     : num 1
